---
title: "GDP Components and contribution of Manufacturing"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, we present economic indicator data using r shiny application.For sample we start with trend of all four components of GDP. 


## GDP components USA
 The four components of gross domestic product are personal consumption, business investment, government spending, and net exports. Consumer spending contributes to 68.4% in 2017,which is ~ $12.6 trillion. While Investments and government spending contributes to the same 17.3% of GDP. The United States imports more than it exports, creating a trade deficit. America still imports a lot of petroleum, despite gains in domestic shale oil production. In 2017, imports subtracted  USD 3.3 trillion, while exports added USD 2.5 trillion. As a result, international trade subtracted USD 859 billion from GDP, which is -3% of real GDP.
 
*Highlights*
1. Consumption and expenditure contribution are growing with a positive growth rate of ~1.5% & ~ 3%  for the last 10 years <br />
2. Investment has been declining for the last 8 years with an average rate of 3.25% <br />
3. Net exports has always been a negative contributor to GDP resulting in huge trade deficit,but atleast its on a trend towards a positive number<br />

```{r eruptions, echo=FALSE}
library(shiny)
library(ggplot2)
library(plotly,warn.conflicts = FALSE)
df1<- read.csv("cig_year.csv")

# Define UI for application that plots features of movies
ui <- fluidPage(
  
  # Sidebar layout with a input and output definitions
  sidebarLayout(
    
    # Inputs
    sidebarPanel(
      
      # Select variable for y-axis
      selectInput(inputId = "y", 
                  label = "Y-axis:",
                  choices = c("value in %"        = "value", 
                              "Year"       = "Year" 
                  ), 
                  selected = "value"),
      
      # Select variable for x-axis
      selectInput(inputId = "x", 
                  label = "X-axis:",
                  choices = c("Year"= "Year"
                  ), 
                  selected = "Year"),
      
      # Select variable for color
      selectInput(inputId = "z", 
                  label = "Color by:",
                  choices = c(
                    "component" = "component"
                  ),
                  selected = "component"),
      sliderInput(inputId = "alpha",label = "Years:",min = 1929,max = 2018,
                  value = c(1967, 2017))
      
      
    ),
    
    # Outputs
    mainPanel(
      plotlyOutput(outputId = "scatterplot")
    )
  )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
    data <- subset(df1,Year >= input$alpha[1] & Year <= input$alpha[2])
    ggplot(data = data, aes_string(x=input$x, y = input$y,
                                   color = input$z)) +
      geom_line()
  
  })
  })
}

shinyApp(ui = ui, server = server)

```

## Manufacturing sector contribution towards GDP
We compare USA contribution of manufacturing with other major economies of the world.The contribution of manufacturing is on a decreasing trend for USA and UK while other leading industrial nations are still have an incresing trend for manufacturing in the last 5 years.
The input slider of years will change the timeline selected for the plot/table. A linear regression line can also be plotted to check the trend of the selected time line.<br/>

*Highlights:-*
1. Manufacturing sector has been on the decline in USA along with other leading economies <br />
2. South Korea is the only one nation which has a positive growth rate in its Manufacuturing contribution towards GDP<br />
3. 

```{r eruptions1, echo=FALSE}
library(shiny)
library(plotly)
df<- read.csv("mfg.csv")


# Define UI for application that plots features of movies
ui <- fluidPage(
  # Create a container for tab panels
  tabsetPanel(
    tabPanel(title = "Plot",plotlyOutput(outputId = "scatterplot")),
  ##for plot and inputs panel
    tabPanel( title = "Inputs",
      numericInput("size", "Point size", 1, 1),
      checkboxInput("fit", "Add line of best fit", FALSE),
      # Select variable for y-axis
      selectInput(inputId = "y",label = "Y-axis:",choices = c("mfg_gdp_%"  = "mfg_gdp","Year" ="Year" 
                  ), 
                  selected = "mfg_gdp"),
      
      # Select variable for x-axis
  selectInput(inputId = "x",label = "X-axis:",choices = c("Year"= "Year"), selected = "Year"),
      ##adding download button
      downloadButton(outputId = "download_data", label = "Download"),
      ####
      selectInput("Country", "Country",choices = c("All", levels(df$Country))),
      # Select variable for color
      selectInput(inputId = "z",label = "Color by:",choices = c("Country" = "Country"),
                  selected = "Country"),
      sliderInput(inputId = "alpha",label = "Years:",min = 1967,max = 2018,
                  value = c(1981, 2017))
      
    ),
 
    # Create "Table" tab
    tabPanel(title = "Table",tableOutput("table"))
  )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  
  # Create the scatterplot object the plotOutput function is expecting
  output$scatterplot <- renderPlotly({
    ggplotly({
    data <- subset(df,Year >= input$alpha[1] & Year <= input$alpha[2])
    if (input$Country != "All") {
      data <- subset( data,Country == input$Country
      )
    }
   p<- ggplot(data = data, aes_string(x = input$x, y = input$y,
                                   color = input$z)) +
      geom_line(size = input$size)
   if (input$fit) {
     p <- p + geom_smooth(method = "lm")
   }
   p
  })
  })
  
  output$table <- renderTable({
    data <- df
    data <- subset(df,Year >= input$alpha[1] & Year <= input$alpha[2])
    if (input$Country != "All") {
      data <- subset( data,Country == input$Country
      )
    }
    data
  })
  # Create a download handler
  output$download_data <- downloadHandler(
    # The downloaded file is named "download.csv"
    filename = "download.csv",
    content = function(file) {
      # The code for filtering the data is copied from the
      # renderTable() function
      data <- df
      data <- subset(df,Year >= input$alpha[1] & Year <= input$alpha[2]
      )
      # Write the filtered data into a CSV file
      write.csv(data, file, row.names = FALSE)
    }
  )
}

# Create a Shiny app object
shinyApp(ui = ui, server = server)


```

Further developements to be made in the report


